Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-07 project/report/paper.tex
minor paper tweaks

\subsection{Generator Failure}
Now, we investigate how our Hierarchical LMS system responds to spontaneous generator failures. 
To this end, we
simulated the case when generator 2 would fail at time 45. Obviously, if the Optimizing LMS were
to run in isolation, it would leave the system unpowered from time 45 to 50. 
Figure~\ref{fig:lsllonefail} shows what would happen if the LL-LMS were to run in 
isolation. Starting at time 45, the LL-LMS sees that generator 2 has failed and it has 
switched to using generator 1 to power both buses according to its priority table. In order
to stay under generator 1's power rating, the LL-LMS sheds a large number of loads on the 
second bus. Figure~\ref{fig:lsolonefail} shows what would happen in a combined Optimizing LMS
LL-LMS system. The Optimizing LMS produces advice to be used from time 40 to 50. Unfortunately,
there is no way for the Optimizing LMS's advice to be aware of the failure at time 45. So, while the advice
from time 40 to 44 is optimal and safe, the advice from 45 to 49 is unsafe. The LL-LMS is
able to see this at time 45 and kicks in, ignoring the unsafe advice from the Optimizing LMS. This
behavior is observed in Figure~\ref{fig:lsolonefail} where from time 45 to 49, a large
number of loads are shed. Then at time 50, the Optimizing LMS reoptimizes by turning on the APU.
Notice the difference in the number of loads shed onward from time 50 in 
Figure~\ref{fig:lsllonefail} and Figure~\ref{fig:lsolonefail}.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/lsllonefail.png}
  \caption{\textbf{LL-LMS Load Shedding -- One Failure}. Notice
  the large amounts of load shedded in order to keep power usage below the power rating
  of generator 1.}
  \label{fig:lsllonefail}
\end{figure}
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/lsolonefail.png}
  \caption{\textbf{Hierarchical LMS Load Shedding -- One Failure}. Notice the
  large number of loads dropped from time 45 to 50 before the Optimizing LMS can reoptimize.}
  \label{fig:lsolonefail}
\end{figure}

>>>>

\subsection{Generator Failure}
Now, we investigate how our Hierarchical LMS system responds to spontaneous generator failures. 
To this end, we
simulated the case when generator 2 would fail at time 45. Obviously, if the Optimizing LMS were
to run in isolation, it would leave the system unpowered from time 45 to 50. 
Figure~\ref{fig:lsllonefail} shows what would happen if the LL-LMS were to run in 
isolation. Starting at time 45, the LL-LMS sees that generator 2 has failed and it has 
switched to using generator 1 to power both buses according to its priority table. In order
to stay under generator 1's power rating, the LL-LMS sheds a large number of loads on the 
second bus. Figure~\ref{fig:lsolonefail} shows what would happen in a combined Optimizing LMS
LL-LMS system. The Optimizing LMS produces advice to be used from time 40 to 50. Unfortunately,
there is no way for the Optimizing LMS's advice to be aware of the failure at time 45. So, while the advice
from time 40 to 44 is optimal and safe, the advice from 45 to 49 is unsafe. The LL-LMS is
able to see this failure at time 45 and kicks in, ignoring the unsafe advice from the Optimizing LMS. This
behavior is observed in Figure~\ref{fig:lsolonefail} where from time 45 to 49, a large
number of loads are shed. Then at time 50, the Optimizing LMS reoptimizes by turning on the APU.
Notice the difference in the number of loads shed onward from time 50 in 
Figure~\ref{fig:lsllonefail} and Figure~\ref{fig:lsolonefail}.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/lsllonefail.png}
  \caption{\textbf{LL-LMS Load Shedding -- One Failure}. Notice
  the large amount of loads shedded in order to keep power usage below the power rating
  of generator 1.}
  \label{fig:lsllonefail}
\end{figure}
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/lsolonefail.png}
  \caption{\textbf{Hierarchical LMS Load Shedding -- One Failure}. Notice the
  large number of loads dropped from time 45 to 50 before the Optimizing LMS can reoptimize.}
  \label{fig:lsolonefail}
\end{figure}
